The contribution of blowing snow to cloud properties and the atmospheric radiative budget over Antarctica

### 2020-10-09 manuscript/manuscript.tex
WIP: Write Introduction

>>>>

Antarctica is the largest body of ice on the planet and it contains the coldest places on Earth.  It contains ice mass equivalent to roughly \textbf{XX m} of global sea level rise, roughly 10 times more than the Greenland Ice Sheet (\textbf{cite XX}). The interior plateau of the Antarctica reaches up to elevations of \textbf{XX m}, and is marked by very cold and dry conditions (\textbf{cite XX}). However, there are marked differences in the present climatic conditions between East and West Antarctica, and especially between the edges and the inner plateau. While West Antarctica, and especially the northwards reaching mountainous Antarctic peninsula receive ample precipitation and are rather cloudy, weather systems never reach the interior of Antarctica, where most of the precipitation falls as diamond dust under extremely cold  "clear" sky conditions (cite XX).

Due to strong radiative cooling in the interior plateau, strong and perpetual katabatic winds emerge, redistributing snow mass from the interior towards the edges and ice shelves, where the up to \textbf{XX m} high plateau slopes steeply towards sea level (\textbf{CITE XX}).
